A comprehensive framework to capture the arcana of neuroimaging analysis

### 2018-10-18 manuscript/manuscript.tex
finalised proof of Arcana for bioRxiv

Interface traits are connected to inputs and outputs of the pipeline by
providing \emph{inputs} and \emph{outputs} keyword arguments to the \emph{add} method. Both
arguments take a dictionary, where the keys of the dictionary are the names of traits of the interface. The
values of the dictionary are 2-tuples each consisting of the name of a data specification
and the format the pipeline expects the data in (i.e. a FileFormat for Fileset specifications or datatype
for Field specifications). If the expected format does not match that of the corresponding data specification
or study input then a conversion node is implicitly connected to the pipeline.
Inputs and outputs that are conditional on parameters or inputs provided to the
study can be set outside of the \emph{add} method using the \emph{connect\_input} or
\emph{connect\_output} methods, respectively.

@@

Any external software packages required by a node should be referenced
in the \emph{requirements} keyword argument as a list of
\emph{Requirement} objects when the node added to the pipeline.
Similarly, the expected memory requirements and
wall time for the node execution should be provided to the keyword arguments
\emph{memory}, and \emph{wall\_time}.

@@

A healthy volunteer was scanned using a 3T Siemens Skyra with a 32-channel head
and neck coil to demonstrate the application of analyses implemented in
Arcana. The protocol was a T1-weighted MPRAGE (1mm contiguous,
matrix size 256x240x192, FOV 256x240x192, TE = 2.13ms, TR, = 2300ms, TI
= 900ms, bandwidth=230Hz/pixel), GRE (1.8 mm contiguous, matrix size
256x232x72, FOV 230x208x130, TE = 20ms, TR, = 30ms,
bandwidth=120Hz/pixel), and diffusion MRI (1.2 mm contiguous, matrix size
110x100x60, FOV 256x240x192, TE = 95ms, TR, = 8200ms, 33 diffusion
directions with b=1500 mm2/s and 3 b=0, bandwidth=781Hz/pixel).

>>>>

Interface traits are connected to inputs and outputs of the pipeline by
providing \emph{inputs} and \emph{outputs} keyword arguments to the \emph{add} method. Both
arguments take a dictionary, where the keys of the dictionary are the names of traits of the interface. The
values of the dictionary are 2-tuples each consisting of the name of a data specification
and the format the pipeline either expects or produces the data in (i.e. a FileFormat for Fileset specifications
or Python datatype for Field specifications). If the expected format does not match that of the
corresponding data specification or study input then a conversion node is implicitly connected
to the pipeline. Inputs and outputs that are conditional on parameters or inputs provided to the
study can be set outside of the \emph{add} method using the \emph{connect\_input} or
\emph{connect\_output} methods, respectively.

@@

Any external software packages required by a node should be referenced
in the \emph{requirements} keyword argument as a list of
\emph{Requirement} objects when the node added to the pipeline.
Similarly, the expected memory requirements in MB and
wall time for the node execution should be provided to the keyword arguments
\emph{memory}, and \emph{wall\_time}.

@@

A healthy volunteer was scanned using a 3T Siemens Skyra with a 32-channel head
and neck coil to demonstrate the application of analyses implemented in
Arcana. The protocol was a T1-weighted MPRAGE (1mm contiguous,
matrix size 256x240x192, FOV 256x240x192, TE = 2.13ms, TR, = 2300ms, TI
= 900ms, bandwidth = 230Hz/pixel), GRE (1.8 mm contiguous, matrix size
256x232x72, FOV 230x208x130, TE = 20ms, TR, = 30ms,
bandwidth = 120Hz/pixel), and diffusion MRI (1.2 mm contiguous, matrix size
110x100x60, FOV 256x240x192, TE = 95ms, TR, = 8200ms, 33 diffusion
directions with b = 1500 mm2/s and 3 b=0, bandwidth = 781Hz/pixel).
